\title{Learning to Draw Vector Graphics: Applying Generative Modeling to Font Glyphs}

\author{Kimberli Zhong}
% If you wish to list your previous degrees on the cover page, use the 
% previous degrees command:
%       \prevdegrees{A.A., Harvard University (1985)}
% You can use the \\ command to list multiple previous degrees
%       \prevdegrees{B.S., University of California (1978) \\
%                    S.M., Massachusetts Institute of Technology (1981)}
\department{Department of Electrical Engineering and Computer Science}

\degree{Master of Engineering in Electrical Engineering and Computer Science}

\degreemonth{June}
\degreeyear{2018}
\thesisdate{May 25, 2018}

%% By default, the thesis will be copyrighted to MIT.  If you need to copyright
%% the thesis to yourself, just specify the `vi' documentclass option.  If for
%% some reason you want to exactly specify the copyright notice text, you can
%% use the \copyrightnoticetext command.  
\copyrightnoticetext{\copyright{} 2018 Massachusetts Institute of Technology. All rights reserved.}

\supervisor{Fr\'edo Durand}{Professor of Electrical Engineering and Computer Science}

\chairman{Katrina LaCurts}{Chair, Master of Engineering Thesis Committee}

\maketitle

\cleardoublepage{}
\setcounter{savepage}{\thepage}
\begin{abstractpage}
\input{abstract}
\end{abstractpage}

\cleardoublepage{}

\section*{Acknowledgments}

This work certainly would not have been possible without the help of my colleagues, friends, and family.

Zoya, you have been indispensable as a mentor, role model, and friend.
Thank you for your unique insights, neverending patience, and delicious food.
Anelise, Sami, Spandan, Nathan, Camilo, and Matt---thank you for providing me feedback when I needed it the most and for making group meetings entertaining and enlightening.
To Fredo, thank you for giving me a chance and the freedom to work on this project.

Mom, Dad, and Billy: I wouldn't be the person I am now without you.
You never cease to amuse and encourage me, and I hope this thesis will make you proud.
And to all my friends I made here at MIT, thank you for always supporting me and making me laugh.
You've made the last four years here unforgettable, and I will cherish our friendships for a long time to come.
